---
title: "Validation Plan for R packages"
format: html
params:
    r_version: "4.4.2"
    main_packages: ""
    extra_packages: ""
    snapshot_date: "" 
    validation_strategy_url: ""
---

# Introduction

This document serves as a Validation Plan for R packages that are to be installed together with R version `r params$r_version`. It is built on the foundations of the [Validation Strategy](`r params$validation_strategy_url`). For any missing package, a time-based snapshot with date `r params$snapshot_date` is used. 

::: {.callout-important}
## Important

The validation plan outlined in this document is very basic and may not be appropriate to be used in a real-world scenario unchanged. It nevertheless can serve as a starting point to develop a workflow around for testing R packages. In many cases the validation plan is combined with a general Impact Analysis and Quality Strategy for the changes made to your system. 
:::

# Package List


```{r}
#| label: main-package-table
#| echo: false

library(gt)

main_packages<-as.data.frame(params$main_packages)

main_packages %>%
  gt() %>%
  tab_header(
    title = "Packages selected for Testing"
  ) %>%
  cols_align(
    align = "left",
    columns = c(name, version, URN)
  ) %>%
  tab_style(
    style = cell_borders(
      sides = "all",
      color = "gray",
      style = "solid",
      weight = px(1)
    ),
    locations = cells_body()
  ) %>%
  opt_row_striping() %>%
  tab_options(
    table.width = pct(100),
    table.font.size = px(12)
  )
```



In order to make `R CMD check` run successfully, the following additional dependencies have been identified that will be installed temporarily. 

```{r}
#| label: extra-package-table
#| echo: false

library(gt)

extra_packages<-as.data.frame(params$extra_packages)


extra_packages %>%
  gt() %>%
  tab_header(
    title = "Extra Packages needed for `R CMD check`"
  ) %>%
  cols_align(
    align = "left",
    columns = c(name, version, URN)
  ) %>%
  tab_style(
    style = cell_borders(
      sides = "all",
      color = "gray",
      style = "solid",
      weight = px(1)
    ),
    locations = cells_body()
  ) %>%
  opt_row_striping() %>%
  tab_options(
    table.width = pct(100),
    table.font.size = px(12)
  )
```
